---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r}
require(tidymodels)
require(tidyverse)
library(tidyverse)
#install.packages("hablar")
#library(hablar)
#install.packages("skimr")
#library(skimr)
#require(tidyverse)
#library(tidyverse)
#library(gapminder)#
#install.packages("hablar")
#library(hablar)
#library(dplyr)
#remove.packages(c("ggplot2", "data.table"))
#install.packages('Rcpp', dependencies = TRUE)
#install.packages('ggplot2', dependencies = TRUE)
#install.packages('data.table', dependencies = TRUE)
library(ggplot2)
#library(dplyr)
#install.packages("zoo")
library(vip)
#install.packages("writexl")
#library(writexl)
#install.packages("see")
```

## Introduction to tidy models 
```{r}
Bank_churners<-read_csv("C:/Users/Lenovo/Downloads/BankChurners.csv")
glimpse(Bank_churners)
Bank_churners%>%head()
summary(Bank_churners)
#skim(Bank_churners)
```

```{r}
hist(Bank_churners$Total_Trans_Ct,prob=TRUE,breaks=100)
lines(density(Bank_churners$Total_Trans_Ct))
```

```{r}
hist(Bank_churners$Total_Revolving_Bal,prob=TRUE,breaks=9)
lines(density(Bank_churners$Total_Revolving_Bal))
```


```{r}
ggplot(data = Bank_churners,
       mapping = aes(x = Customer_Age,color = Card_Category)) +geom_histogram(binwidth = 0.8) +facet_wrap(~ Card_Category) +labs(title =
"Customer age vs Card category by Attrition Flag",x = "Customer Age",y = "Count") +
  scale_color_discrete(name = "Card Category") +theme_light() +facet_wrap(~ Card_Category) +facet_grid(. ~ Attrition_Flag)
```




```{r}
Bank_churners$Attrition_Flag <- as.numeric(factor(Bank_churners$Attrition_Flag))

set.seed(123)

# Create a split object
Bankchurners_split <- initial_split(Bank_churners, prop = 0.90, 
                                   strata = Attrition_Flag)

# Build training data set
Bankchurners_training <- Bankchurners_split %>% 
                        training()

# Build testing data set
Bankchurners_test <- Bankchurners_split %>% 
                    testing()
```

```{r}
lm_model <- linear_reg() %>% 
            set_engine('lm') %>% # adds lm implementation of linear regression
            set_mode('regression')
```

```{r}
lm_fit <- lm_model %>% 
          fit(Attrition_Flag ~ . , data=Bankchurners_training)
# View lm_fit properties
lm_fit
```

```{r}

names(lm_fit)
```



To print a summary of our model, we can extract `fit` from `lm_fit` and pass it to the `summary()` function. We can explore the estimated coefficients, F-statistics, p-values, residual standard error (also known as RMSE) and R2 value.

However, this feature is best for visually exploring our results on the training data since the results are returned as a data frame.



```{r}
summary(lm_fit$fit)
```




We can use the `plot()` function to obtain diagnostic plots for our trained regression model. Again, we must first extract the `fit` object from `lm_fit` and then pass it into `plot()`. These plots provide a check for the main assumptions of the linear regression model.



```{r fig.width = 10, fig.height = 10}
par(mfrow=c(2,2)) # plot all 4 plots in one

plot(lm_fit$fit, 
     pch = 16,    # optional parameters to make points blue
     col = '#006EA1')

```

### Tidy Training Results

To obtain the detailed results from our trained linear regression model in a data frame, we can use the `tidy()` and `glance()` functions directly on our trained `parsnip` model, `lm_fit`.

The `tidy()` function takes a linear regression object and returns a data frame of the estimated model coefficients and their associated  F-statistics and p-values.

The `glance()` function will return performance metrics obtained on the training data such as the R2 value (`r.squared`) and the RMSE (`sigma`). 



```{r}
# Data frame of estimated coefficients
tidy(lm_fit)
```



```{r}
# Performance metrics on training data
glance(lm_fit)
```



We can also use the `vip()` function to plot the variable importance for each predictor in our model. The importance value is determined based on the F-statistics and estimate coefficents in our trained model object.



```{r}
vip(lm_fit)
```


```{r}
predict(lm_fit, new_data = Bank_churners)
```
```{r}
ggplot(data = Bank_churners,
       mapping = aes(x = Total_Trans_Amt, y = Total_Trans_Ct)) +
  geom_point(color = '#006EA1') +
  geom_abline(intercept = 0, slope = 1, color = 'orange') +
  labs(title = 'Linear Regression Results - Total_Trans_Ct & Total_Trans_Amt',
       x = 'Total_Trans_Amt',
       y = 'Total_Trans_Ct')
```
